ResultsNPS

### 2019-09-10 R/scripts/resultsNPS.Rmd
added presentation to DISC, many changes in R reports and graphs, some code corrections on batch instances in python

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(reticulate)
library(tidyverse)
library(knitr)
library(magrittr)
library(ggplot2)
use_virtualenv('~/Documents/projects/OPTIMA/python/venv/', required = TRUE)
current_dir = getwd()
# print(current_dir)
py_discover_config()
quant_max <- 0.95
size <- params$size
aux_compare <- function(table){
    table %>% 
    gather(key='indicator', value="value", -experiment) %>% 
    spread(experiment, value) %>% 
    mutate(dif_abs = cuts - base,
           dif_perc = (dif_abs/ base*100) %>% round(2))

}

```{python}
import pandas as pd
import numpy as np

import sys, os
opt_path = './'
# opt_path = '../'
rel_path_python = '{}../python/'.format(opt_path)
path = os.path.join(r.current_dir, rel_path_python)
# print(path)
sys.path.insert(1, path)

import package.batch as ba
import package.params as params

import stochastic.params as sto_params
import scripts.compare_stochastic as compare_sto

# This is read now as a paramer in the YAML (above).
# size = 'small'  # choose small, medium or large
# df = compare_sto.get_instances[r.size]()

################# manual alternative...
# exp_list = ['IT000125_20190808', 'IT000125_20190729']
# df = compare_sto.get_df_comparison(exp_list)
# df = df[df.scenario == 'numparalleltasks_2']

exp_list = ['IT000125_20190808', 'IT000125_20190812']
df = compare_sto.get_df_comparison(exp_list).reset_index()
# df = df[df.scenario == 'numparalleltasks_3']
df = df.query("scenario == 'numparalleltasks_3' or experiment==1")
################# manual alternative...

name_change = dict(experiment=[0, 1], experiment2=["cuts", "base"])
name_change = pd.DataFrame(name_change)
df = df.merge(name_change, on='experiment').drop('experiment', axis=1).rename(columns=dict(experiment2='experiment'))

@@

summary_stats <- 
    py$df %>% 
    mutate(sol_code = if_else(is.na(sol_code), 2, sol_code)) %>% 
    group_by(experiment) %>%
    summarise(Infeasible = sum(sol_code==-1),
              IntegerFeasible=sum(sol_code==2),
              IntegerInfeasible=sum(sol_code==0),
              Optimal=sum(sol_code==1),
              total_instances = n()) %>% 
  aux_compare

summary_stats %>% kable

@@

t1 <- 
    py$df %>% 
    filter(sol_code==1) %>% 
    group_by(instance) %>%
    mutate(min_value = min(best_solution),
           dist_min = best_solution - min_value,
           dist_min_perc = (best_solution - min_value)/abs(min_value)*100
           )
t1_rel <- 
    t1 %>% 
    select(instance, experiment, dist_min_perc) %>% 
    spread(key=experiment, value=dist_min_perc) %>% 
    drop_na() %>% use_series(cuts)

t1_abs <- 
    t1 %>% 
    select(instance, experiment, dist_min) %>% 
    spread(key=experiment, value=dist_min) %>% 
    drop_na() %>% use_series(cuts)

@@

```{r}
qplot(t1_rel[t1_rel<20], xlab='Relative gap (in %) among optimal solutions.')
```

@@

quality_perf <-
    py$df %>% 
    filter(sol_code>=1) %>%
    select(instance, experiment, best_solution) %>% 
    spread(experiment, best_solution) %>% 
    drop_na() %>% 
    mutate(dif_perc = ((cuts-base)/ base*100) %>% round(2))

  mean_dif <- quality_perf$dif_perc %>%  mean
  per_cut <- sum(quality_perf$dif_perc<0)/length(quality_perf$dif_perc)

@@

```{r}
filtered_q_perf <- quality_perf %>% filter(between(dif_perc, -5, 5))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%) have been taken out to help better visualize it.

@@

comparison_table <- 
    py$df %>% 
    filter(sol_code>=1) %>% 
    group_by(instance) %>%
    filter(n()==2) %>% 
    ungroup() %>% 
    select(instance, experiment, time) %>% 
    spread(experiment, time) %>% 
    arrange(base) %>% 
    mutate(instance = row_number()) %>% 
    gather(key = 'experiment',  value='time', -instance)

comparison_table_reorder <- 
    comparison_table %>% 
    group_by(experiment) %>% 
    arrange(experiment, time) %>% 
    mutate(percentage = row_number()/n()*100)

@@

The following graph shows the solving times in seconds for each of the `r t1 %>% distinct(instance) %>% nrow` instances were an integer solution was found in both cases. In red are the times for the base model. In green the times for the model with the added cuts.

@@

comparison_table <- 
    py$df %>% 
    filter(sol_code==1) %>% 
    group_by(instance) %>% 
    filter(n()==2) %>% 
    select(experiment, instance, time) %>%
    group_by(experiment) %>% 
    summarise(time_mean = mean(time), 
              time_medi = median(time)) %>% 
    aux_compare

@@

```{r infeasible_list}

infeasible_instances <- py$df %>% filter(sol_code==-1) %>% distinct(instance)
```

@@

```{r infeasible}
infeasible_stats <- 
    py$df %>% 
    inner_join(infeasible_instances) %>% 
    filter(experiment=="base") %>% 
    summarise(Infeasible = sum(sol_code==-1),
              IntegerFeasible=sum(sol_code==2),
              IntegerInfeasible=sum(sol_code==0),
              Optimal=sum(sol_code==1),
              total_instances = n()) %>% 
    gather(key='status', 'number') %>% 
  filter(number>0)

infeasible_stats %>% kable
```

@@

```{r soft_constraints}
errors_stats <- 
    py$df %>% 
    filter(sol_code>=1) %>% 
    mutate(errors = replace_na(errors, 0)) %>% 
    group_by(experiment) %>% 
    summarise(errors_mean = mean(errors),
              errors_q95 = quantile(errors, quant_max),
              errors_medi = median(errors)) %>% 
    aux_compare

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')

quant_max <- 0.95
size <- params$size

# alternative 1:
# exp_list <- c('IT000125_20190808', 'IT000125_20190812')
# df_original <- compare_sto$get_df_comparison(exp_list)
# df_original %<>% filter(scenario=='numparalleltasks_3' | experiment==1)
# alternative 2:
# compare_sto <- get_compare_sto()
# df_original <- compare_sto$get_instances[[size]]()
# df <- df_original %>% mutate(experiment=if_else(experiment==0, 'cuts', 'base'))
# alternative 3:
df <- do.call(params$size, args=list())
# df <- get_4_tasks_aggressive()

@@

summary_stats <- get_summary(df)
summary_stats %>% kable

@@

t1 <- get_quality_degr(df)
t1_rel <- t1 %>% filter(experiment=='cuts') %>% use_series(dist_min_perc)
t1_abs <- t1 %>% filter(experiment=='cuts') %>% use_series(dist_min)

@@

```{r}
qplot(t1_rel_filt, xlab='Relative gap (in %) among optimal solutions.')
```

@@

quality_perf <- get_quality_perf(df)
mean_dif <- quality_perf$dif_perc %>%  mean
per_cut <- sum(quality_perf$dif_perc<0)/length(quality_perf$dif_perc)

@@

```{r}
filtered_q_perf <- quality_perf %>% filter(between(dif_perc, -10, 10))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%) have been taken out to help better visualize it.

@@

comparison_table <- get_time_perf_integer(df)

comparison_table_reorder <- get_time_perf_integer_reorder(df)

@@

The following graph shows the solving times in seconds for each of the `r comparison_table %>% distinct(instance) %>% nrow` instances were an integer solution was found in both cases. In red are the times for the base model. In green the times for the model with the added cuts.

@@

comparison_table <- get_time_perf_optim(df)

@@

```{r infeasible_list}
infeasible_instances <- get_infeasible_instances(df)
infeasible_stats <- get_infeasible_stats(df)
```

@@

```{r infeasible}
infeasible_stats %>% kable
```

@@

```{r soft_constraints}
errors_stats <- get_soft_constraints(df, quant_max)
